---
title: "Statistics Applications II <br> Assignment 1"
author: "S20510"
output:
  html_document: default
  pdf_document: default
---


### What Is Variance?

In statistics, variance measures **variability** from the average or mean.It is calculated by taking the differences between each number in the data set and the mean, then squaring the differences to make them positive, and finally dividing the sum of the squares by the number of values in the data set.

Variance is calculated by using the following formula:

$\sigma^2 = \sum_{i = 1}^{n} \frac{(x_{i}- \overline{x} )^2}{N}$

**where**

$x_{i}$ = Each value in the data set

$\overline{x}$ = Mean of all values in the data set

*N* = Number of values in the data set

Explore more from:

[links]<https://www.investopedia.com/terms/v/variability.asp>

```{r}
ln <- iris$Petal.Length
var(ln)
```



The variance of the Petal.length is 3.116278.

```{r echo=FALSE}
plot(x = iris$Petal.Length, y = iris$Petal.Width,
     xlab = "Petal Length", ylab = "Petal Width",
     main = "Iris Dataset: petal Length vs petal Width")
```









